Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-06-09 pirouette_supplement.tex
@Giappo was right: figure 26 in section 8.11 was not updated yet. Let @richelbilderbeek check all other figures, see #103

\begin{figure}[H]
  \includegraphics[width=0.98\textwidth]{pirouette_example_26/errors.png}
  \caption{Aggregate error distributions for 20 replicates. Here each true tree is generated by a BD process. For the inference we used instead a Yule tree prior. This took 9 hours to compute.}
\end{figure}

\giovanni{This is the example one of the reviewer was referring to. The figure that was present before (still present in the overleaf files) looked actually quite different from the one on the repo (\url{https://raw.githubusercontent.com/richelbilderbeek/pirouette_example_26/master/errors.png}). I changed it with the one found there. In case you think this is wrong you can revert it back.}

>>>>

\begin{figure}[H]
  \includegraphics[width=0.98\textwidth]{pirouette_example_26/errors.png}
  \caption{
    Aggregate error distributions for 20 replicates. Here each true 
    tree is generated by a BD process. For the inference we used instead a 
    Yule tree prior. This took 9 hours to compute.
  }
\end{figure}
